\section{Key Features}
\begin{enumerate}
    \item \textbf{Spatial Scalability}: Blocktree achieves unbounded growth through its tree-like structure, splitting branches periodically using the Fiedler vector of a latency-based Laplacian matrix~\cite{ng2001spectral}. This enables potentially thousands of independent branches, each processing transactions in parallel, scaling seamlessly across planetary distances with minimal latency overhead.

    \item \textbf{AI-Driven DeFi}: Blocktree supports autonomous financial systems by enabling AI agents to execute decentralized finance (DeFi) operations, such as trading or lending, directly on-chain. The isolated branch architecture, with subsecond block times (e.g., 0.2 seconds), ensures ultra-high transaction throughput, allowing machine-to-machine economies to operate without human intervention.

    \item \textbf{Edge DApp Support}: By clustering nodes via latency-aware spectral methods, Blocktree minimizes communication delays for decentralized applications (DApps) at the network edge, ideal for real-time use cases like IoT or gaming. Subsecond block times deliver near-instant transaction validation, optimized for proximity-based networks.

    \item \textbf{Interstellar Finance}: Blocktree’s design facilitates secure, scalable transactions across vast distances, supporting space economies with BKT, a cryptocurrency mined uniformly across branches. Branch autonomy mitigates light-speed delays (e.g., 3–24 minutes Earth-to-Mars), enabling reliable commerce for extraterrestrial settlements.

    \item \textbf{Permissionless Network}: Built on a Proof of Work (PoW) protocol~\cite{nakamoto2008bitcoin}, Blocktree allows any node with computational power to mine BKT without barriers, ensuring open access and decentralization. This fosters universal adoption, from Earth to interstellar nodes.
\end{enumerate}