\section{Roadmap}
Blocktree’s development is a journey to redefine blockchain scalability, adaptability, and decentralization for artificial intelligence, edge computing, and interstellar economies. Initiated in 2024, the project builds on a foundation of innovative design and open-source collaboration, with milestones to bring its vision to reality across Earth and beyond.

\begin{itemize}
    \item \textbf{2024: Conceptual Design}: Established the Blocktree architecture, introducing a tree-like structure with periodic, topology-driven splits using the Fiedler vector~\cite{ng2001spectral}. Developed initial simulations to validate subsecond block times and latency-based clustering, laying the groundwork for AI-driven DeFi and edge DApps.

    \item \textbf{Early -chartered2025: Prototype Development}: Refine the Proof of Work (PoW) protocol~\cite{nakamoto2008bitcoin} and spectral clustering algorithms, targeting subsecond block times for high-frequency transactions. Release early prototypes demonstrating branch splitting and BKT mining, inviting community feedback to enhance scalability and adaptability.

    \item \textbf{Mid-2025: Beta Deployment}: Launch a beta network with multiple branches, enabling real-world testing of AI agents executing DeFi operations and edge DApps processing IoT or gaming transactions. Optimize Fiedler vector clustering for terrestrial latency, preparing for interstellar scenarios with simulated Earth-Mars delays (3–24 minutes).

    \item \textbf{2026: Interstellar Testnets}: Deploy testnets simulating interplanetary conditions, validating branch autonomy and BKT fungibility across vast distances. Integrate advanced AI and edge DApp frameworks, fostering machine economies and real-time applications. Expand open-source contributions to refine the network for global and extraterrestrial adoption.

    \item \textbf{Beyond 2026: Ecosystem Growth}: Scale Blocktree into a universal platform for decentralized finance, edge computing, and space economies. Support Martian commerce, autonomous AI markets, and IoT networks through thousands of branches, each processing thousands of transactions per second. Drive continuous innovation with a global community, building a blockchain that spans the cosmos.
\end{itemize}

This roadmap reflects Blocktree’s commitment to a scalable, permissionless future, evolving through iterative development and collaboration to meet the needs of Earth, Mars, and beyond.